\vspace{-2.5cm}A generative model for urban firm networks

### 2019-11-15 extended_abstract.tex
Update on Overleaf.

As a matter of validation, the model is implemented for real data for Europe joining Functional Urban Areas with the Global Human Settlement Database for cities and their characteristics, with the AMADEUS database produced by the Bureau Van Dijk on ownership links between firms in Europe between 2010 and 2018 at postcode level in all types of sectors. Calibration is done using a genetic NSGA2 algorithm, finding the parameter values giving network trajectories closest to reality. First results show in particular a role of the path-dependency parameter confirming the relevance of this complex generative model. Further work is needed to get more conclusions from this experiment but we already show the feasibility of model calibration on real data.

Several scenarios are considered taking into consideration the current and future economic challenges, such as those given by Brexit. This way, the model may be applied in future work to concrete policy questions.

>>>>

As a matter of validation, the model is implemented for real data for Europe joining Functional Urban Areas with the Global Human Settlement Database for cities and their characteristics, with the AMADEUS database produced by the Bureau Van Dijk on ownership links between firms in Europe between 2010 and 2018 at postcode level in all types of sectors. Calibration is done using a genetic NSGA2 algorithm, finding the parameter values giving network trajectories closest to reality. First results show in particular a role of the path-dependency parameter confirming the relevance of this complex generative model. Further work is needed to get more interpretations from this experiment, but our study demonstrates the feasibility of model calibration on real data. Several scenarios are considered taking into consideration the current and future economic challenges, such as those given by Brexit. The model may be applied in future work to assess policy issues and recommendations.
